Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-03 nge.tex
Section 5.0 - refinement.

\jhanote{not sure MPI script is optimal description or ambiguous.}\mtnote{Is
what we used in the previous section(s) to designate what PanDA Broker submits
to Titan's Torque batch system. Job is already used for what is pulled from
PanDA server.} Multiple generations would also relax two assumptions of the
current execution model: knowing the number of simulations before submitting the
MPI script, and having a fixed number of events per simulation (100 at the
moment). Pilots would enable the scheduling of simulations independently from
whether they were available at the moment of submitting the pilot. Further,
simulations with a varying number of events could be scheduled on a pilot,
depending on the amount of remaining walltime and the distribution of execution
time per event, as shown in \S\ref{ssec:panda_titan},
Figure~\ref{fig:100event-distrib}. These capabilities would increase the
efficiency of the PanDA Broker when there is a large difference between the
number of cores and walltime.

@@

Pilots can offer a payload-independent scheduling interface while hiding the
mechanics of coordination and communication among multiple worker nodes. This
could eliminate the need for packaging payload into MPI scripts within the
broker, greatly simplifying the submission process. This simplification would
also enable the submission of different types of payload, without having to
develop a specific PBS script for each payload. The submission process would
also be MPI-independent, as MPI is used for coordination among multiple worker
nodes, not by the payload. \jhanote{candidate for compression/contraction into
earlier paragraph(s)}

@@

\jhanote{Alternative: "NGE is a runtime system to execute heterogeneous and
dynamically determined tasks that constitute workloads." This definition put the
focus on tasks and not workloads, which is a level above in the RADICAL
conceptual layer diagram.}\mtnote{Done.} NGE is a runtime system to execute
heterogeneous and dynamically determined tasks that constitute workloads.
Fig.~\ref{fig:arch- overview} illustrates its current architecture as deployed
on Titan: the two management modules (Pilot and Unit) represent a simplified
version of the PanDA Broker while the agent module is the pilot submitted to
Titan and executed on its worker nodes. The communication between PanDA Broker
and PanDA Server is abstracted away as it is not immediately useful to evaluate
the performance and capabilities of a pilot on Titan.

@@

NGE exposes an API for the application  \jhanote{workload management?} layer to
describe workloads (Fig.~\ref{fig:arch-overview}, green squares) and pilots
(Fig.~\ref{fig:arch-overview}, red circles), and to instantiate a PilotManager
and a UnitManager.   The PilotManager submits pilots to Titan's Torque
\jhanote{for consistency should we say Moab?}\mtnote{Moab = Scheduler; Torque =
Batch system.} batch system via SAGA API (Fig.~\ref{fig:arch-overview}, dash
arrow), as done by PanDA Broker to submit MPI scripts. Once scheduled, the
pilot's Agent is bootstrapped on Titan's MOM node and \jhanote{the Agent's
Executors on the} the Agent's Executors on the worker nodes, and the
UnitManager schedules units to the Agent's Scheduler (Fig.~\ref{fig:arch-
overview}, solid arrow). The Agent's Scheduler schedules the units on one or
more Agent's Executor for execution. The Agent's executors can manage one or
more worker nodes, depending on performance evaluations. The UnitManager and the
Agent communicate via a database that is instantiated on one of Titan's DTN so
as to be reachable by both modules.

% A similar approach would be used to enable PanDA Broker to schedule pilots
% instead of MPI scripts.\mtnote{Rewrite this after checking it with
% Andre.}
\jhanote{In the interest of space and clarity, I would  remove the last
sentence of this para. And merge the first sentence with the para
above.}\mtnote{Done.}

>>>>

% \jhanote{not sure MPI script is optimal description or ambiguous.}\mtnote{Is
% what we used in the previous section(s) to designate what PanDA Broker submits
% to Titan's PBS batch system. Job is already used for what is pulled from
% PanDA server.}

Multiple generations would also relax two assumptions of the current execution
model: knowing the number of simulations before submitting the MPI script, and
having a fixed number of events per simulation (100 at the moment). Pilots
would enable the scheduling of simulations independently from whether they
were available at the moment of submitting the pilot. Further, simulations
with a varying number of events could be scheduled on a pilot, depending on
the amount of remaining walltime and the distribution of execution time per
event, as shown in \S\ref{ssec:panda_titan}, Figure~\ref{fig:100event-
distrib}. These capabilities would increase the efficiency of the PanDA Broker
when there is a large difference between the number of cores and walltime.

@@

Pilots can offer a payload-independent scheduling interface while hiding the
mechanics of coordination and communication among multiple worker nodes. This
could eliminate the need for packaging payload into MPI scripts within the
broker, greatly simplifying the submission process. This simplification would
also enable the submission of different types of payload, without having to
develop a specific PBS script for each payload. The submission process would
also be MPI-independent, as MPI is used for coordination among multiple worker
nodes, not by the payload.

@@

NGE is a runtime system to execute heterogeneous and dynamically determined
tasks that constitute workloads. Fig.~\ref{fig:arch- overview} illustrates its
current architecture as deployed on Titan: the two management modules (Pilot
and Unit) represent a simplified version of the PanDA Broker while the agent
module is the pilot submitted to Titan and executed on its worker nodes. The
communication between PanDA Broker and PanDA Server is abstracted away as it
is not immediately useful to evaluate the performance and capabilities of a
pilot on Titan.

@@

NGE exposes an API for the application  \jhanote{workload management?} layer
to describe workloads (Fig.~\ref{fig:arch-overview}, green squares) and pilots
(Fig.~\ref{fig:arch-overview}, red circles), and to instantiate a PilotManager
and a UnitManager.   The PilotManager submits pilots to Titan's PBS  batch
system via SAGA API (Fig.~\ref{fig:arch-overview}, dash arrow), as done by
PanDA Broker to submit MPI scripts. Once scheduled, the pilot's Agent is
bootstrapped on Titan's MOM node and \jhanote{the Agent's Executors on the}
the Agent's Executors on the worker nodes, and the UnitManager schedules units
to the Agent's Scheduler (Fig.~\ref{fig:arch- overview}, solid arrow). The
Agent's Scheduler schedules the units on one or more Agent's Executor for
execution. The Agent's executors can manage one or more worker nodes,
depending on performance evaluations. The UnitManager and the Agent
communicate via a database that is instantiated on one of Titan's DTN so as to
be reachable by both modules.

% \jhanote{for consistency should we say Moab?}\mtnote{Moab = Scheduler; Torque
% = Batch system. I used PBS Batch System because it makes easier to speak about
% both the system and the script submitted to it.}

% A similar approach would be used to enable PanDA Broker to schedule pilots
% instead of MPI scripts.\mtnote{Rewrite this after checking it with
% Andre.}
% \jhanote{In the interest of space and clarity, I would  remove the last
% sentence of this para. And merge the first sentence with the para
% above.}\mtnote{Done.}
